---
title: "simpleRegress"
author: "Wayne Jarvis"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict WEIGHT other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

## CONCLUSION AND RANKING

According to the data I collected, these are the models that predict weight and other variables from worst to best. This was done with ARS and RSE.

1. WEIGHT~CHEST: RSE: 33.08 and ARS: 0.9262
2. WEIGHT~NECK: RSE: 43.91 and ARS: 0.87
3. WEIGHT~LENGTH: RSE: 61.83 and ARS: 0.7423
4. WEIGHT~HEADLENGTH: RSE: 67.81 and ARS: 0.69
5. WEIGHT~HEADWIDTH: RSE: 76.41 and ARS: 0.6064
6. WEIGHT~AGE: RSE: 81.47 and ARS: 0.5526






